packages

### 2024-11-05 install_packages.Rmd
install new packages for Tutorial 3
add broom.mixed package
add packages for sims.Rmd

@@

install.packages("devtools")
devtools::install_github("jmgirard/standist")
# 
install.packages(c("brms", "tidybayes", "bayesplot", "future"))
```

@@

```{r}
#install.packages("lme4", "nlme")
```

>>>>

Next, packages for simulation (Figures 1, 2, and 3)

```{r}
install.packages(c("faux","ggpmisc","truncnorm"))
```

@@

install.packages("devtools")
devtools::install_github("jmgirard/standist")
# 
install.packages(c("brms", "tidybayes", "bayesplot", "future"))

install.packages("broom.mixed")
```

@@

```{r}
install.packages("lme4", "nlme")
```
